Formatting Instructions \\for Authors Using \LaTeX{}

### 2016-05-30 doc/paper.tex
random ideas

@@

@@

In the Moses toolchain, the {\small \tt mkcls} component \mycitep{och:98} performs this process in reverse, binning words into automatically-generated equivalence classes to alleviate data sparsity issues.
% USUALLY alignment only, CAN be applied to translation... http://www.statmt.org/moses/?n=Advanced.Models#ntoc6
With some effort, you can use these bins during steps other than alignment, although this is not done by default.
...
Moreover, as they are upstream of GIZA++, these bins are constructed at the lexical level, not the phrase level, whereas the templates described below can make substitutions at the level of larger constituents and phrases.

@@

aha, yoshua bengio's "curse of dimensionality" - becomes a blessing?  
Unlike many machine learning tasks (image recognition, finance), NLP data are purely artificial/manmade.  New paradigm?  Not enough attention has been paid IMO to semi-automated corpus generation.  Well, typical approaches are paid, like Mechanical Turk... but there is a vast untapped source of data in the form of student problem sets, in the spirit of reCAPTCHA (citation!?)

>>>>

AHA, what you've really done is traded in-house linguists who coded rules for outsourced linguists who churn out data.
Is that really optimal?
Better off bringing corpus writers back in-house, where possible.

@@

disproportionate amount of attention being paid to the machine learning
not enough attention being paid to the corpora themselves

@@

In the Moses toolchain, the {\small \tt mkcls} component \mycitep{och:98} performs this process in reverse, binning words into automatically-generated equivalence classes to alleviate data sparsity issues.
% USUALLY alignment only, CAN be applied to translation... http://www.statmt.org/moses/?n=Advanced.Models#ntoc6
With some effort, you can use these bins during steps other than alignment, although this is not done by default.
...
Moreover, as they are upstream of GIZA++, these bins are constructed at the lexical level, not the phrase level, whereas the templates described below can make substitutions at the level of larger constituents and phrases.
Furthermore, it is run at training time and cannot help with unknown words at test time (is this true??)
The only real cure for unknown words is moar data

@@

aha, yoshua bengio's "curse of dimensionality" - becomes a blessing?  
Unlike many machine learning tasks (image recognition, finance), NLP data are purely artificial/manmade.  New paradigm?  Not enough attention has been paid IMO to semi-automated corpus generation.  Well, typical approaches are paid, like Mechanical Turk... but there is a vast untapped source of data in the form of student problem sets, in the spirit of reCAPTCHA (citation!?)
NLP is unique among machine learning tasks in that humans are not only consumers, but also producers of data - the alpha and the omega, the beginning and the end.
MT is further unique among NLP in that both input and output representations are widely accepted (modulo dialectical variations) - the source and target languages themselves.
People on the street would agree to the representations.
